SDR enhancement by clouds

### 2024-03-12 article/article.Rmd
Commit 2024-03-12 15:13
Commit 2024-03-12 19:22

@@

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data for AOD and water column from AERONET [@Giles2019; @Buis1998]. Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
We have simulated the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, on $0.2^\circ$ SZA's step. 
With combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].

@@

For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA. We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA. 
For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.

@@

six criteria in order to evaluate random multiples of 25 days with some characteristics

@@

>>>>

$\text{GHI}_\text{i}$: measured one minute global horizontal irradiance

$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance

$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance

@@

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period, to be used as reference.
For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data of AOD and water column from the AERONET monitoring network [@Giles2019; @Buis1998].
Our site participate in AERONET, where we operate a Cimel photometer since 2003.
We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
We simulated the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.
For the atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of atmospheric clearness for the climatological conditions of the site.

Furthermore, to account for the Sun's variability in our one-minute GHI measurements, we adjusted the model's input spectrum integral to the one of the the TSI provided by NOAA.
Finally, we adjusted for the effect of Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
Thus, the modeled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.

@@

 We applied the effect of

@@

six criteria 
in order to evaluate random groups of about 20 to 30 days with some characteristics

@@

```{r echo=FALSE, fig.cap="Distribution of "}
knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
```

```{r echo=FALSE, fig.cap="Distribution of "}
knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
```
